\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}

\name{Marouani Nesrine}

\address{
\textbf{Cloud DevOps Engineer} \\
AWS • Kubernetes • CI/CD • Docker • Terraform • Automation
}

\address{
+(216) 22484553 • Tunis, Tunisia \\
\href{mailto:nesrine.marouani22@hotmail.com}{nesrine.marouani22@hotmail.com} \\
\href{https://www.linkedin.com/in/nesrine-marouani-547651143/}{LinkedIn} •
\href{https://myresumy.netlify.app}{Portfolio}
}

\begin{document}

%----------------------------------------------------------------------------------------
% OBJECTIVE
%----------------------------------------------------------------------------------------
\begin{rSection}{OBJECTIVE}

\textbf{DevOps Engineer with 4+ years of experience} in Kubernetes orchestration, CI/CD automation, and multi-environment platform management. Strong background in on-premise and hybrid infrastructures, with hands-on experience designing and deploying \textbf{cloud-native architectures on AWS}, including \textbf{EKS-based platforms, secure IAM configurations, and CI/CD pipelines}. Actively progressing toward \textbf{AWS Solutions Architect Associate} to strengthen cloud architecture expertise.

\end{rSection}


%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}

\textbf{Bachelor of Software Engineering} \hfill November 2024 \\
Private Higher School of Technology and Engineering \hfill Tunis, Tunisia \\

\vspace{0.1em}

\textbf{Bachelor's Degree in Computer Science Applied to Management} \hfill 2014 -- 2017 \\
Faculty of Economics and Management (FSEGT), University of Tunis \hfill Tunis, Tunisia \\

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }

DevOps \& CI/CD 
& GitHub Actions (Repos, Pipelines), Jenkins, Git, CI/CD automation \\

Containers \& Orchestration 
& Docker, Kubernetes, Helm, Services, Ingress, Namespaces \\

Cloud Platforms 
& AWS (EKS, EC2, IAM, VPC, ALB, ECR, S3, CloudWatch), Azure (fundamentals) \\

Infrastructure as Code 
& Terraform (hands-on projects, provisioning, state management) \\

Monitoring \& Observability 
& Prometheus, Grafana, CloudWatch, New Relic, alerting, log analysis \\

Operating Systems 
& Linux (Ubuntu, Debian, RedHat), Windows Server \\

Networking \& Security 
& HAProxy, Nginx, SSL/TLS, IAM concepts \\

Collaboration \& Agile 
& Jira, Confluence, Scrum \\

Languages 
& French (B2), English (B2), Arabic (native) \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{WORK EXPERIENCE}

\textbf{DevOps Engineer} \hfill October 2022 -- 2025 \\
Septeo \hfill Tunis, Tunisia \\

\begin{itemize}
\itemsep -3pt
\item Designed, implemented, and maintained \textbf{CI/CD pipelines} using \textbf{GitHub Actions} for multiple applications and environments.
\item Automated build, test, validation, and deployment workflows using pipelines and \textbf{Shell scripting}.
\item Deployed and operated containerized applications using \textbf{Docker, Kubernetes, and Helm}.
\item Collaborated with development teams to define reliable delivery workflows and release strategies.
\item Implemented monitoring and alerting using \textbf{Prometheus, Grafana, and New Relic}.
\item Handled incidents, troubleshooting, and \textbf{root cause analysis} related to pipelines and infrastructure.
\item Ensured availability and stability of CI/CD platforms across test, staging, and pre-production environments.
\item Actively contributed to continuous improvement of delivery performance and platform reliability.
\item Participated in \textbf{Agile/Scrum ceremonies} using Jira and Confluence.
\end{itemize}

\vspace{0.4em}

\textbf{Infrastructure \& Operations Responsibilities}
\begin{itemize}
\itemsep -3pt
\item Administered and supported \textbf{Linux (Ubuntu, Debian, RedHat)} and \textbf{Windows Server} systems.
\item Operated monitoring and alerting platforms to proactively detect and resolve incidents.
\item Performed log analysis and post-incident reviews.
\item Managed storage systems (LVM, file systems) and supported databases (\textbf{PostgreSQL, MySQL}).
\end{itemize}

\vspace{0.4em}

\textbf{IT System and DevOps Technician} \hfill 2020 -- September 2022 \\
Network Associate \hfill Tunis, Tunisia \\

\begin{itemize}
\itemsep -3pt
\item Containerized enterprise applications (Alfresco ECM, WordPress) using \textbf{Docker}.
\item Assisted in CI/CD automation and application deployment workflows.
\item Performed application migrations between virtual machines.
\item Deployed applications to production environments and ensured operational support.
\item Provided troubleshooting, incident resolution, and technical documentation.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS \& KEY ACHIEVEMENTS}

\textbf{AWS Cloud-Native Application Platform (Personal Project – 2025)}
\begin{itemize}
\itemsep -3pt
\item Designed a \textbf{multi-AZ AWS architecture} using VPC, public/private subnets, routing, and security groups.
\item Deployed containerized \textbf{React frontend and Spring Boot backend} on \textbf{Amazon EKS}.
\item Built and managed container images using \textbf{Docker and Amazon ECR}.
\item Implemented \textbf{Application Load Balancer (ALB) Ingress Controller}.
\item Configured \textbf{IAM Roles for Service Accounts (IRSA)} for secure pod-level access.
\item Built \textbf{CI/CD pipelines with GitHub Actions} to automate build and deployment to EKS.
\item Enabled logging and monitoring using \textbf{Amazon CloudWatch}.
\end{itemize}

\vspace{0.3em}

\textbf{Multi-Tenant HR Platform Industrialization} \hfill Final Year Project 2024
\begin{itemize}
\itemsep -3pt
\item Designed and deployed a Kubernetes-based multi-tenant architecture.
\item Automated deployments using Helm charts.
\item Implemented monitoring and alerting with Grafana.
\item Produced installation and operational documentation.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------
\begin{rSection}{CERTIFICATIONS}

\begin{itemize}
\itemsep -3pt
\item \textbf{AWS Cloud Practitioner (Foundational)} — Certified 
(\href{https://www.credly.com/badges/6618a670-75d7-4602-ad23-bf817696286b/public_url}{Credly Badge})
\item \textbf{AWS Solutions Architect – Associate} (in progress)
\end{itemize}

\end{rSection}

\end{document}
